\documentclass{resume}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Artur Kopytin} % Your name
\position{Full Stack Engineer}
\technologies{Java, Spring Boot, TypeScript, React.js, Redux}
\address{+972 53 332-8460 \\ Tel Aviv, Israel} 
\address{
\href{https://github.com/Asnvir}{github.com/Asnvir} \\ 
\href{https://www.linkedin.com/in/artur-kopytin/}{linkedin.com/in/artur-kopytin/}\\ 
\href{mailto:artur.kop97@gmail.com} {artur.kop97@gmail.com}
}

\begin{document}

\begin{rSection}{Summary}

I am a \textbf{Full Stack} Engineer  with \textbf{4 years} of \textbf{experience} in open-source projects and a recent graduate of \textbf{Afeka College of Engineering}, where I earned a degree in \textbf{Software Engineering}. During my time at Afeka, I developed fullstack applications, which you can view in the \textbf{projects} section or on my \href{https://github.com/Asnvir}{GitHub} page. These projects utilize technologies such as \textbf{Java, Spring Boot, JavaScript, TypeScript, React.js, Redux, HTML, CSS, Tailwind CSS,} and \textbf{databases} like\textbf{ MongoDB, Firebase, MySQL,} and \textbf{PostgreSQL}.

I started my career as a \textbf{Network and Threat Support Specialist} at Bynet Business, where I built a strong foundation in network infrastructure and security. This experience has been crucial in \textbf{securing} the \textbf{applications} I develop, using technologies like \textbf{JSON Web Tokens (JWT)} and \textbf{Keycloak} to ensure robust security.

I am confident that I would be a valuable asset to your company, both as a developer and as a team member. Thank you for considering my application.
\end{rSection}


\vspace{5pt}


\begin{rSection}{Skills}

\begin{tabularx}{\textwidth}{@{}>{\textbullet\hspace{\labelsep}\bfseries}l X@{}}
\vspace{0.25em}
\hspace{\labelsep}Frontend: & HTML, CSS, Tailwind CSS, JavaScript, TypeScript, React.js, RESTful API \\
\vspace{0.25em}
\hspace{\labelsep}Backend: & Java, RxJava, Spring, Hibernate, JSON Web Tokens (JWT), Keycloak, Docker, JUnit, MongoDB, Firebase, MySQL, PostgreSQL, Git, OOP, SOLID \\
\vspace{0.25em}
\hspace{\labelsep}Soft Skills: & Communication, Problem-solving, Adaptability, Creativity, Attention to detail \\
\vspace{0.25em}
\hspace{\labelsep}Languages: & Hebrew - Native, Russian - Native, Ukrainian - Native, English - Fluent
\end{tabularx}
\end{rSection}

\vspace{5pt}
\begin{rSection}{Education}

\begin{tabular}{@{}p{0.8\textwidth}p{0.2\textwidth}}
  {\bf Bachelor of Science (B.Sc.) in Software Engineering}, Afeka College of Engineering & \hfill 2020 - 2024\hspace*{1em} \\
  & \hfill \\
  % \vspace{0.5em}
  {\bf Frontend Developer}, Hilel IT School & \hfill 2022 - 2023\hspace*{1em} \\
  \begin{itemize}
      \item GPA 100. Link to certificate - \href{https://certificate.ithillel.ua/view/81706976}{click me} 
  \end{itemize}
\end{tabular}

\end{rSection}


% \vspace{5pt}


\begin{rSection}{PROJECTS}

\textbf{VolunNear} 
\href{https://github.com/Asnvir/VolunNear-frontend}{Frontend Repo, } 
\href{https://github.com/Asnvir/VolunNear-backend}{Backend Repo} \hfill 2024\hspace*{1em}
\begin{itemize}
    \item VolunNear connects volunteers with organizations, making it easy for both sides to find and manage opportunities. With a user-friendly interface, it streamlines the process, saving time and ensuring a smooth experience for all involved.
    \item \textbf{Technologies Used:} Java, Spring Boot, JWT, MySQL, Docker, React, Typescript, TanStack Query, Chakra UI.
\end{itemize}

\vspace{0.25em}

\textbf{\href{https://github.com/Asnvir/HealthApp}{HealthApp}} \hfill 2024\hspace*{1em}

\begin{itemize}
    \item HealthApp is an innovative platform that revolutionizes personal health and nutrition management through tools and features for informed decisions about diet, fitness, and wellness.
    \item \textbf{Technologies Used:} Java, Spring Boot, MongoDB, Docker, Swagger, JUnit.
\end{itemize}

\vspace{0.25em}

\textbf{\href{https://github.com/Asnvir/React-TS-RickMorty}{Search App - Rick and Morty}}  \hfill 2023\hspace*{1em} 

\begin{itemize}
    \item A React application leveraging the Rick and Morty API to enable multifaceted character and episode searches.
    \item \textbf{Technologies Used:} React, TypeScript, Redux, Tailwind CSS.
\end{itemize}

\end{rSection}


\vspace{80pt}

\begin{rSection}{Experience}

\textbf{Network and Threat Support Specialist} \hfill 2018 - 2020\\
Bynet Business \hfill \textit{Tel Aviv, Israel}
 \begin{itemize}
    \item Monitored network infrastructure in real-time and provided immediate response to security threats, ensuring the integrity of information systems.
    \item Managed installation, configuration, and maintenance of network equipment, including routers, switches, and firewalls, to optimize performance and security.
 \end{itemize}
\end{rSection}



\vspace{10pt}

\begin{rSection}{Military service}
	\textbf{Network and Threat Support Specialist} \hfill 2016 - 2018\\
	Israel Defense Forces 
	\begin{itemize}
		\item A volunteer soldier with the title of Network and Threat Support Specialist.
	\end{itemize}
\end{rSection} 


\vspace{10pt}

\begin{rSection}{Awards}
\begin{itemize}
 		\item\textbf{\href{https://drive.google.com/file/d/1QWiVud-gSK4n_YLskh-mxVn0zGRxDvHW/view?usp=sharing}{Military Recognition as a Volunteer Soldier (Hebrew - Miztayen Aluf)}}
		\item Received a Certificate of Merit for exceptional dedication as a volunteer and lone soldier in the Israel Defense Forces (IDF), awarded by the Commander of the Southern Command.
	\end{itemize}
\end{rSection} 

\vspace{10pt}

\begin{rSection}{Volunteering work}
	\textbf{Personal Guidence of Lone Soldiers} \hfill 2020 - present\\
	Ach Gadol (Big Brother) for Lone Soldiers
	\begin{itemize}
		\item As a lone soldier in the past, I help my soldiers to understand the military system in Israel and to receive all the rights they deserve, while being closely guiding them.
	\end{itemize}
\end{rSection} 




\end{document}