\documentclass{resume}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Artur Kopytin} % Your name
\position{Fullstack Engineer}
\technologies{Java, Spring Boot, React.js, TypeScript, Docker, Git, MongoDB}
\address{+972 53 332-8460 \\ Tel Aviv, Israel} 
\address{
\href{https://github.com/Asnvir}{github.com/Asnvir} \\ 
\href{https://www.linkedin.com/in/artur-kopytin/}{linkedin.com/in/artur-kopytin/}\\ 
\href{mailto:artur.kop97@gmail.com} {artur.kop97@gmail.com}
}

\begin{document}

\begin{rSection}{Summary}

% I am a  \textbf{Fullstack Engineer} with expertise in designing and developing web applications. Proficient in both frontend and backend technologies, including \textbf{JavaScript},  \textbf{TypeScript}, \textbf{React.js}, \textbf{Java} and \textbf{Spring Boot}. Strong background in \textbf{RESTful APIs}, \textbf{OOP}, and \textbf{SOLID} principles. Adept at working in dynamic environments, ensuring efficient and scalable solutions.

I am a \textbf{Fullstack} Web Developer with \textbf{4 years} of experience in open-source projects, specializing in building \textbf{secure}, \textbf{responsive}, and \textbf{dynamic web applications}.

My \textbf{backend} expertise includes modern technologies like \textbf{Spring Boot}, \textbf{Java} as the core of the application, \textbf{Hibernate} – which simplifies how data is stored and retrieved from databases, \textbf{Docker} – enabling applications to run consistently across different environments, \textbf{Git} – a system for tracking changes in code. I also have extensive experience in designing and implementing \textbf{RESTful API}s for efficient communication between systems. I adhere to \textbf{OOP} and \textbf{SOLID} principles to ensure that the \textbf{code} is \textbf{modular}, \textbf{maintainable}, and \textbf{scalable}. I also work with \textbf{databases} such as \textbf{MongoDB}, \textbf{Firebase}, \textbf{MySQL}, and \textbf{PostgreSQL}.

On the \textbf{frontend}, I excel in \textbf{JavaScript} and \textbf{TypeScript} as the foundation of the application, and libraries like \textbf{React.js} (for creating interactive user interfaces), \textbf{Redux} (for managing application state), \textbf{ HTML/CSS} (for structuring and styling web pages), and the \textbf{Tailwind CSS} framework (for designing user-friendly interfaces). I am currently expanding my skills with \textbf{Next.js} (a framework for building fast, server-rendered web applications), and you can see these technologies in action in my projects.

My career began as a \textbf{Network and Threat Support Specialist} at Bynet Business, where I developed a solid foundation in network infrastructure and security. This experience has been invaluable in securing the applications I develop, with technologies like \textbf{JSON Web Tokens (JWT)} (a method for securely transmitting information) and \textbf{Keycloak} (a system for managing user identities and access) being among the tools I use to ensure robust security.

I am now seeking my next challenge, where I can continue to grow and make a meaningful impact.
\end{rSection}


\vspace{5pt}


\begin{rSection}{Skills}

\begin{tabularx}{\textwidth}{@{}>{\textbullet\hspace{\labelsep}\bfseries}l X@{}}
\vspace{0.25em}
\hspace{\labelsep}Frontend: & HTML, CSS, Tailwind CSS, JavaScript, TypeScript, React.js, RESTful API \\
\vspace{0.25em}
\hspace{\labelsep}Backend: & Java, RxJava, Spring, Hibernate,JSON Web Tokens (JWT), Keycloak, Docker, JUnit, MongoDB, Firebase, MySQL, PostgreSQL, Git, OOP, SOLID \\
\vspace{0.25em}
\hspace{\labelsep}Soft Skills: & Communication, Problem-solving, Adaptability, Creativity, Attention to detail \\
\vspace{0.25em}
\hspace{\labelsep}Languages: & Hebrew - Native, Russian - Native, Ukrainian - Native, English - Fluent
\end{tabularx}
\end{rSection}

\vspace{5pt}
\begin{rSection}{Education}

\begin{tabular}{@{}p{0.8\textwidth}p{0.2\textwidth}}
  {\bf Bachelor of Science (B.Sc.) in Software Engineering}, Afeka College of Engineering & \hfill 2020 - 2024\hspace*{1em} \\
  & \hfill \\
  % \vspace{0.5em}
  {\bf Frontend Developer}, Hilel IT School & \hfill 2022 - 2023\hspace*{1em} \\
  \begin{itemize}
      \item Completed an intensive JavaScript and React course, gaining practical skills in front-end development, including OOP, DOM, REST API, and React library.
  \end{itemize}
\end{tabular}

\end{rSection}


% \vspace{5pt}


\begin{rSection}{PROJECTS}

\textbf{VolunNear} 
\href{https://github.com/Asnvir/VolunNear-frontend}{Frontend Repo, } 
\href{https://github.com/Asnvir/VolunNear-backend}{Backend Repo}
\begin{itemize}
    \item VolunNear is an application designed to bridge the gap between volunteers and organizations in need. With its user-friendly interface and powerful features, the platform makes the user experience smooth, fast, and enjoyable, saving valuable time for everyone involved. For volunteers, it’s incredibly easy and convenient to find opportunities that match their preferences, while organizations can effortlessly find and manage volunteers, as well as coordinate volunteer activities.
    \item \textbf{Technologies Used:} Java, Spring Boot, JWT, MySQL, Docker, React, Typescript, TanStack Query, Chakra UI.
\end{itemize}

\vspace{0.25em}

\textbf{\href{https://github.com/Asnvir/HealthApp}{HealthApp}}

\begin{itemize}
    \item HealthApp is an innovative platform that revolutionizes personal health and nutrition management through tools and features for informed decisions about diet, fitness, and wellness.
    \item \textbf{Technologies Used:} Java, Spring Boot, MongoDB, Docker, Swagger, JUnit.
\end{itemize}

\vspace{0.25em}

\textbf{\href{https://github.com/Asnvir/React-TS-RickMorty}{Search App - Rick and Morty}}

\begin{itemize}
    \item A React application leveraging the Rick and Morty API to enable multifaceted character and episode searches.
    \item \textbf{Technologies Used:} React, TypeScript, Redux, Tailwind CSS.
\end{itemize}

\end{rSection}


\vspace{5pt}

\begin{rSection}{Experience}

\textbf{Network and Threat Support Specialist} \hfill Dec 2018 - Aug 2020\\
Bynet Business \hfill \textit{Tel Aviv, Israel}
 \begin{itemize}
    \item Monitored network infrastructure in real-time and provided immediate response to security threats, ensuring the integrity of information systems.
    \item Managed installation, configuration, and maintenance of network equipment, including routers, switches, and firewalls, to optimize performance and security.
 \end{itemize}
\end{rSection}



\vspace{10pt}


\begin{rSection}{Awards}

\textbf{\href{https://drive.google.com/file/d/1QWiVud-gSK4n_YLskh-mxVn0zGRxDvHW/view?usp=sharing}{Military Recognition as a Volunteer Soldier (Hebrew - Miztayen Aluf)}} \\
Received a Certificate of Merit for exceptional dedication as a volunteer and lone soldier in the Israel Defense Forces (IDF), awarded by the Commander of the Southern Command.

\end{rSection} 

\end{document}